\sclearpage\beginsong{Bad Bad Leroy Brown}[by={Jim Croce}]
\beginverse*{\nolyrics Intro: \[G] \[D7]         \brk
}\endverse
\beginverse
Well, the \[G]south side of Chicago\brk
Is the \[A7]baddest part of town.\brk
And if you \[B7]go down there\brk
You better \[C]just beware of a \[D7]man name of \[C]Leroy Bro\[G]wn.\[D7]\brk
Now, \[G]Leroy more than trouble,\brk
You see he \[A7]stand about 'bout six foot four.\brk
All the \[B7]downtown ladies cal\[C]l him "treetop lover."
All the \[D7]men just \[C]call him sir.\[G]  \[D7]         \brk
\endverse
\beginchorus
And he's \[G]bad, bad, Leroy Brown,\brk
The \[A7]baddest man in the whole damn town.\brk
\[B7]Badder than old King \[C]Kong\brk
And \[D7]meaner than a \[C]junkyard do\[G]g. \[D7]         \brk
\endchorus
\beginverse
Now, \[G]Leroy, he a gambler,\brk
and he \[A7]like his fancy clothes.\brk
And he \[B7]like to wave \[C]diamond rings\brk
in front of \[D7]every\[C]body's \[G]nos\[D7]e\brk
He got a \[G]custom Continental.\brk
He got an \[A7]Eldorado too.\brk
He got a \[B7]thirty-two gun in his \[C]pocket for fun.\brk
He got a \[D7]razor \[C]in his \[G]shoe.\[D7]\brk
\endverse
\,\\[0.7cm]
\textbf{R:} And he's bad ...
\,\\[0.1cm]
\beginverse
Well, \[G]Friday 'bout a week ago,\brk
\[A7]Leroy's shootin' dice.\brk
And at the \[B7]edge of the bar sat a \[C]girl name of Doris\brk
and \[D7]oh, that \[C]girl look \[G]nice\[D7]\brk
Well, he \[G]cast his eyes upon her\brk
and the \[A7]trouble soon began.\brk
And \[B7]Leroy Brown, he learned a \[C]lesson 'bout messin'\brk
with the \[D7]wife of a \[C]jealous \[G]man \[D7]         \brk
\endverse
\,\\[0.7cm]
\textbf{R:} And he's bad ...
\,\\[0.1cm]
\beginverse
Well, the \[G]two men took to fightin'\brk
And when they \[A7]pulled them from the floor,\brk
\[B7]Leroy looked like a \[C]jigsaw puzzle with a \[D7]couple of \[C]pieces \[G]gone\[D7].\brk
\endverse
\beginchorus
And he's \[G]bad, bad, Leroy Brown,\brk
The \[A7]baddest man in the whole damn town.\brk
\[B7]Badder than old King Kon\[C]g\brk
And \[D7]meaner than a \[C]junkyard do\[G]g. \[D7]         \brk
And he's \[G]bad, bad, Leroy Brown,\brk
The \[A7]baddest man in the whole damn town.\brk
\[B7]Badder than old King Kon\[C]g\brk
And \[D7]meaner than a \[C]junkyard do\[G]g.\brk
\endchorus
\endsong