\sclearpage\beginsong{Hey There Delilah}[by={Plain White T's}]
\beginverse*{\nolyrics Intro: 
\[D]  \[F#m]    \[D]  \[F#m]         \brk
}\endverse
\beginverse
\[D]Hey there Delilah, what's it \[F#m]like in New York City? \brk
I'm a \[D]thousand miles away, but girl to\[F#m]night you look so pretty, \brk
Yes you \[Bm]do, \[G]Time Square can't \[A]shine as bright as \[Bm]you, \brk
I swear it's \[A]true.\brk
\[D]Hey there Delilah, don't you \[F#m]worry about the distance, \brk
I'm right \[D]there if you get lonely, give this \[F#m]song another listen, \brk
Close your \[Bm]eyes, \[G]listen to my \[A]voice it's my dis\[Bm]guise, \brk
I'm by your \[A]side.\brk
\endverse
\beginchorus
\[D]Oh it's what you do to \[Bm]me, \[D]Oh it's what you do to \[Bm]me,    \[A]         \brk
\[D]Oh it's what you do to \[Bm]me, \[D]Oh it's what you do to \[Bm]me, \brk
What you do to \[D]me.\brk
\endchorus
\beginverse
\[D]Hey there Delilah, I know \[F#m]times are getting hard, \brk
But just be\[D]lieve me girl some day, I'll pay the \[F#m]bills with this guitar, \brk
We'll have it \[Bm]good, \[G]we'll have the \[A]life we knew we \[Bm]would, \brk
My word is \[A]good.\brk
\[D]Hey there Delilah, I've got \[F#m]so much left to say, \brk
If every \[D]simple song I wrote to you, would \[F#m]take your breath away, \brk
I'd write it \[Bm]all, \[G]even more in \[A]love with me you'd \[Bm]fall, \brk
We'd have it \[A]all.\brk
\endverse
\beginchorus
\[D]Oh it's what you do to \[Bm]me, \[D]Oh it's what you do to \[Bm]me,   \[A]         \brk
\[D]Oh it's what you do to \[Bm]me, \[D]Oh it's what you do to \[Bm]me,   \[A]         \brk
\endchorus
\beginverse*{\nolyrics [Bridge]: 
\[G]A thousand miles seems pretty far, but \[A]they've got planes and trains and cars, \brk
\[D]I'd walk to you if I had no other \[Bm]way \brk
\[G]Our friends would all make fun of us, and \[A]we'll just laugh along because, \brk
We \[D]know that none of them have felt this \[Bm]way, \brk
\[G]Delilah I can promise you, that \[A]by the time that we get through, \brk
The \[Bm]world will never ever be the same, and you're to \[A]blame.\brk
}\endverse
\beginverse
\[D]Hey there Delilah you be \[F#m]good, and don't you miss me, \brk
Two more \[D]years and you'll be done with school, and \[F#m]I'll be making history, \brk
Like I \[Bm]do, \[G]you'll know it's \[A]all because of \[Bm]you, \brk
\[G]We can do what\[A]ever we want \[Bm]to, \brk
\[G]Hey there De\[A]lilah here's to \[Bm]you, this one's for \[A]you.\brk
\endverse
\beginverse*{\nolyrics [Outro]: 
\[D]Oh it's what you do to \[Bm]me, \[D]Oh it's what you do to \[Bm]me,   \[A]         \brk
\[D]Oh it's what you do to \[Bm]me, \[D]Oh it's what you do to \[Bm]me, \brk
What you do to \[D]me.\brk
\[Bm]good \[D]tab a\[Bm]nd all\[D] but \[Bm]u nee\[D]d to \[Bm]look \[D]over u\brk
}\endverse\endsong