\sclearpage\beginsong{Honey Honey}[by={ABBA}]
\beginverse\[F]Honey, honey, how you thrill me, ah\[Bb]-hah, honey, honey.\brk
\[F]Honey, honey, nearly kill me, ah\[Bb]-hah, honey, honey.\brk
\[F]I'd heard about you be\[Dm]fore..I \[F]wanted to know some \[Dm]more.\brk
And \[F]now I know what they \[Dm]mean, you're a love \[Bb]machine..\brk
\[C7]oh, you make me dizzy.\brk
\[F]Honey, honey, let me feel it, ah-\[Bb]hah, honey, honey.\brk
\[F]Honey, honey, don't conceal it, ah-\[Bb]hah, honey, honey.\brk
The \[F]way that you kiss good\[Dm]night..(the\[F] way that you kiss me goo\[Dm]dnight.)\brk
The \[F]way that you hold me \[Dm]tight..(the \[F]way that you're holding me \[Dm]tight.)\brk
I \[F]feel like I wanna \[Dm]sing when you do your \[Bb]thing. \[C7]         \brk
\[Cm]I don't wanna hurt you, \[F]baby, I \[Bb]don't wanna \[Dm]see you \[Gm]cry.\brk
\[Cm]So stay on the ground, girl, \[F]you better not get too \[Bb]high.\brk
But \[Fm]I'm gonna stick to you, \[Bb]boy, you'll \[Eb]never get \[Bb]rid of \[Ab]me.\brk
There's \[F]no other place in this \[A#]world where I rather \[Gm]would \[C7]be.\brk
\[F]Honey, honey, touch me, baby, ah-\[Bb]hah, honey, honey.\brk
\[F]Honey, honey, hold me, baby, ah-\[Bb]hah, honey, honey.\brk
You \[F]look like a movie \[Dm]star.(You \[F]look like a movie \[Dm]star.)\brk
But \[F]I know just who you \[Dm]are.(\[F]I know just who you \[Dm]are.)\brk
And, \[F]honey, to say the \[Dm]least, you're a dog-gone \[Bb]beast\[C7].\brk
\[Cm]So stay on the ground, \[F]girl, you better not get too \[Bb]high.\brk
There's \[F]no other place in this \[A#]world where I rather \[Gm]would \[C7]be.\brk
\[F]Honey, honey, how you thrill me, ah\[Bb]-hah, honey, honey.\brk
\[F]Honey, honey, nearly kill me, ah-\[Bb]hah, honey, honey.\brk
\[F]I'd heard about you be\[Dm]fore..I \[F]wanted to know some \[Dm]more.\brk
And \[F]now I know what they \[Dm]mean, you're a love \[Bb]machine\[C7]..(Fade.)\brk
\endverse\endsong