\sclearpage\beginsong{Wonderwall}[by={Oasis}]
\capo{2}
\beginverse*{\nolyrics Intro:    \[Em]  \[G]   \[Dsus4]     \[A7sus4]        \[Em]  \[G]   \[Dsus4]       \[A7sus4]         \brk
}\endverse
\beginverse
\[Em]Today is \[G]gonna be the day\brk
That they're \[Dsus4]gonna throw it back to \[A7sus4]you,\brk
\[Em]By now you \[G]should have somehow\brk
Rea\[Dsus4]lized what you gotta \[A7sus4]do.\brk
\[Em]I don't believe that \[G]anybody \[Dsus4]feels the way I \[A7sus4]do\brk
About you \[C]no\[Dsus2]w.      \[A]         \brk
\endverse
\beginverse
\[Em]Back beat, the \[G]word is on the street\brk
That the \[Dsus4]fire in your heart is \[A7sus4]out.\brk
\[Em]I'm sure you've \[G]heard it all before,\brk
But you \[Dsus4]never really had a \[A7sus4]doubt.\brk
\[Em]I don't believe that \[G]anybody \[Dsus4]feels the way I \[A7sus4]do\brk
About you \[Em]now\[G].   \[Dsus2]     \[A]         \brk
\endverse
\beginverse*{\nolyrics [Bridge]: 
And \[C]all the roads we \[D]have to walk are \[Em]winding,\brk
And \[C]all the lights that \[D]lead us there are \[Em]blinding.\brk
\[C]There are many \[D]things that I would \[G]like to say to you,\brk
\[G]But I don't know \[A7sus4]how.    \[A7]         \brk
}\endverse
\beginchorus
Because \[C]may\[Em7]be,   \[G]         \brk
You're \[G]gonna be the one that \[C]saves me,\[Em7]   \[G]         \brk
And \[Em7]after \[C]all\[Em7],     \[G]         \brk
You're my \[G]wonder\[C]wal\[Em7]l.    \[G]         \brk
\endchorus
\beginverse
\[Em]Today was \[G]gonna be the day,\brk
But they'll \[Dsus4]never throw it back to \[A7sus4]you.\brk
\[Em]By now you \[G]should have somehow\brk
Real\[Dsus4]ized what you're not to \[A7sus4]do.\brk
\[Em]I don't believe that \[G]anybody \[Dsus4]feels the way I \[A7sus4]do,\brk
About you \[Em]now.\[G]   \[Dsus2]     \[A]         \brk
\endverse
\beginverse*{\nolyrics [Bridge]: 
And \[C]all the roads that \[D]lead you there were \[Em]winding,\brk
And \[C]all the lights that \[D]light the way are \[Em]blinding.\brk
\[C]There are many \[D]things that I would \[G]like to say to you,\brk
\[G]But I don't know \[A7sus4]how.    \[A7]         \brk
}\endverse
\beginchorus
Because \[C]may\[Em7]be,   \[G]         \brk
You're \[G]gonna be the one that \[C]saves me,\[Em7]   \[G]         \brk
And \[G]after \[C]all\[Em7],     \[G]         \brk
You're my \[G]wonder\[C]wal\[Em7]l.    \[G] \[Em]         \brk
\endchorus
\beginverse*{\nolyrics [Outro]: 
I said m\[C]aybe,  \[Em7]     \[G]         \brk
You're \[Em7]gonna be the one that \[C]saves me, \[Em7]     \[G]         \brk
You're \[Em7]gonna be the one that \[C]saves me, \[Em7]     \[G]         \brk
You're \[Em7]gonna be the one that \[C]saves me  \[Em7]     \[G] \[Em7]         \brk
   \[C] \[Em]    \[G] \[Em]    \[C] \[Em]    \[G] \[Em7]         \brk
}\endverse\endsong