\sclearpage\beginsong{You Cant Hurry Love}[by={The Supremes}]
\beginverse
I ne\[G]ed love, love, to e\[C]ase my mind,         \[G]         \brk
I \[Bm]need to find\[Em], find,      s\[Am]omeone to call mine. \[D]But mama said:\brk
\endverse
\beginchorus
You can't\[G] hurry love, no,\[C] you just have to \[G]wait.\brk
S\[Bm]he said, love don't com\[Em]e eas\[Am]y, it's a game of giv\[D]e and take.\brk
Yo\[G]u can't hurry love\[C], no, you just hav\[G]e to wait,\brk
you\[Bm] got \[Em]to trust, give it tim\[Am]e, no matter how\[D] long it takes.\brk
\endchorus
\beginverse
But how man\[Bm]y heartaches must I stand,\brk
before I f\[Em]ind a love to let me live again.\brk
Right now the on\[Am]ly thing that keeps me hangin' on,\brk
whe\[D]n I feel my strength, yeah, it's almost \[D7]gone.\brk
\endverse
\beginchorus
You can't\[G] hurry love, no, \[C]you just have to w\[G]ait.\brk
S\[Bm]he said, love don't com\[Em]e ea\[Am]sy, it's a game of gi\[D]ve and take.\brk
\[G]How long must I wait, how\[C] much more can\[G] I take,\brk
b\[Bm]efore \[Em]loneliness \[Am]will cause my heart, hea\[D]rt to break?\brk
\endchorus
\beginverse
No, I ca\[Bm]n't bear to live my life alone,\brk
I gro\[Em]w impatient for a love to call my own.\brk
But when\[Am] I feel that I, I can't go on,\brk
\[D]these precious words keep \[D7]me hanging on.I remember,(mama said):\brk
\endverse
\beginchorus
Y\[G]ou can't hurry love, no\[C], you just have to\[G] wait.\brk
She\[Bm] said, love don't come\[Em] easy\[Am], it's a game of give\[D] and take.\brk
Yo\[G]u can't hurry love, no,\[C] you just have to \[G]wait.\brk
Sh\[Bm]e sai\[Em]d trust, give it time,\[Am] no matte\[D]r how long it\[G] takes.\brk
\endchorus
\beginverse
No, love,\[G] love, don't com\[C]e easy, \[G]         \brk
but\[Bm] I keep o\[Em]n waiting, a\[Am]ntici\[D]pating \brk
f\[G]or that soft voice, to talk to\[C] me at ni\[G]ght,\brk
for\[Bm] some te\[Em]nder arms, t\[Am]o hold me t\[D]ight.\brk
I kee\[G]p waiting, I keep\[C] on waiti\[G]ng,\brk
But \[Bm]it ain't\[Em] easy,       \[Am]  it ain't easy\[D]. But mama said :\brk
\endverse
\beginchorus
Y\[G]ou can't hurry lov\[C]e, no, you just ha\[G]ve to wait.\brk
Sh\[Bm]e said trust, g\[Em]ive it time\[Am], no matter how \[D]long it takes.\brk
Y\[G]ou can't hurry lov\[C]e, no, you just ha\[G]ve to wait.\brk
She\[Bm] said, love don't come \[Em]easy,\[Am] it's a game of give \[D]and  
\endchorus\endsong